---
title: "HW3"
author: "ShibeiXu"
date: "2021/10/19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r load package,echo=FALSE,include=FALSE}
devtools::install_github("p8105/p8105.datasets",force = TRUE)
```
```{r load instacart data,include=FALSE}
library(p8105.datasets)
library(tidyverse)
library(patchwork)
library(ggridges)
knitr::opts_chunk$set(echo=TRUE,warning = FALSE,fig.width = 8,fig.height = 6,out.width = "90%")
data("instacart")
```
### Short Description
there are `r dim(instacart)[2]` variables and `r dim(instacart)[1]` observations in this dataset. It contains details including `user id`: customer identifier, `order id`: order identifier, `product id`: product identifier, `product name`, `reordered` if it is reordered or not. Also, in the local store, there are `r dim(distinct(instacart, department))[1]` departments.

### Answers to question
1.There are `r dim(distinct(instacart, aisle))[1]` aisles in the store. And among them, "`r (instacart %>% group_by(aisle) %>% summarise(item_sum = n()) %>% arrange(desc(item_sum)))[1,1]`" ordered the most.

2.
```{r}
instacart %>% 
  group_by(aisle) %>%
  summarize(n_obs = n())%>%
  filter(n_obs>10000)%>%
  ggplot(aes(x = aisle,y=n_obs)) +
  geom_bar(stat='identity') +
  scale_y_log10() +
  labs(x = "aisles", 
       y = "log10 of total number of items", 
       title = "Item ordered by aisle") +
  coord_flip()
```
3.
```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(item_sum = n()) %>% 
  group_by(aisle) %>% 
  mutate(item_rank = min_rank(desc(item_sum))) %>% 
  filter(item_rank == 1) %>% 
  knitr::kable(digits = 1)
```

4.
```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  spread(key = order_dow, value = mean_hour) %>% 
  rename(Sunday = "0", Monday = "1", Tuesday = "2", Wednesday = "3", Thursday = "4", Friday = "5", Saturday = "6") %>% 
  knitr::kable(digit = 1)
```
### Question 2
```{r load package and data set}
library(p8105.datasets)
library(tidyverse)
library(patchwork)
data("brfss_smart2010")
```
```{r data cleaning and tidy,include=FALSE}
brfss =
  brfss_smart2010 %>%
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Poor", "Fair", "Good", "Very good", "Excellent"))%>%
  mutate(response=as_factor(response))%>%
  arrange(desc(response))
```
Answers to question 2 

1. `r names(which(brfss %>% filter(year == 2002) %>% distinct(locationabbr, locationdesc) %>% select(locationabbr) %>% table() >= 7))` states were observed at least 7 locations in 2002.`r names(which(brfss %>% filter(year == 2010) %>% distinct(locationabbr, locationdesc) %>% select(locationabbr) %>% table() >= 7))`states were observed at least 7 locations in 2010 

2.
```{r}
brfss %>%
  filter(response=="Excellent")%>%
  group_by(year, locationabbr) %>%
  summarise(mean_value = mean(data_value)) %>%
  ggplot(aes(x = year, y = mean_value, group = locationabbr, color = locationabbr)) +
  geom_line() +
  labs(
    y = "mean observatons",
    title = " mean observations by state"
  ) 
```

3.

```{r}
brfss %>%
  filter(year %in% c("2006","2010"), locationabbr == "NY") %>%
  ggplot(aes(x=response,y=data_value,color=response))+
  geom_boxplot()+
  facet_grid(.~year)
```
### Question 3
1.
```{r}
accel=read_csv("accel_data.csv")%>%
  janitor::clean_names()%>%
  pivot_longer(activity_1:activity_1440,names_to = "activitiy_day",values_to = "activity_counts")%>%
  mutate(daytype=ifelse(day=="Sunday"|day=="Saturday","weekend","weekday"))%>%
  mutate(activity_counts=as.integer(activity_counts))
```
there are `r dim(accel)[2]` variables and `r dim(accel)[1]` observations in this dataset. It contains details including `week`: week identifier, `day id`: date identifier, `daytype`: identify if it is weekday(Monday to Friday) or weekend (Saturday to Sunday). The original activity is pivot into `activity_counts`and `activity_day` .

2.
```{r}
accel%>%
group_by(day)%>%
summarize(total=sum(activity_counts))%>%
knitr::kable(digits = 1)
```
The activity in Wednesday and Friday is significantly higher than the activity counts in Saturday.

```{r}
accel%>%
  ggplot(aes(x=activitiy_day,y=activity_counts,color=day))+
  geom_point(alpha=.2)+
  geom_smooth(aes(group=day))+
  labs(
    title="24 hour activity accrose each day",
    x="Hour",
    y="Activity")
```
In this conclude that the activity on Friday morning is the highest while the activity on Sunday afternoon is the second highest. The activity around noon is the lowest accrose the day.
