---
title: "HW3"
author: "ShibeiXu"
date: "2021/10/19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r load package,echo=FALSE,include=FALSE}
devtools::install_github("p8105/p8105.datasets",force = TRUE)
```
```{r load instacart data,include=FALSE}
library(p8105.datasets)
library(tidyverse)
library(patchwork)
library(ggridges)
data("instacart")
```
### Short Description
there are `r dim(instacart)[2]` variables and `r dim(instacart)[1]` observations in this dataset. It contains details including `user id`: customer identifier, `order id`: order identifier, `product id`: product identifier, `product name`, `reordered` if it is reordered or not. Also, in the local store, there are `r dim(distinct(instacart, department))[1]` departments.

### Answers to question
1.There are `r dim(distinct(instacart, aisle))[1]` aisles in the store. And among them, "`r (instacart %>% group_by(aisle) %>% summarise(item_sum = n()) %>% arrange(desc(item_sum)))[1,1]`" ordered the most.

2.
```{r, fig.height=60,fig.width=10}
instacart %>% 
  select(aisle) %>% 
  filter(aisle>10000)%>%
  ggplot(aes(x = factor(aisle,levels=names(sort(table(aisle)))))) +
  geom_bar() +
  scale_y_log10() +
  labs(x = "aisles", 
       y = "log10(total number of items)", 
       title = "number of items ordered in each aisle") +
  coord_flip()
 
```
3.
```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(item_num = n()) %>% 
  group_by(aisle) %>% 
  mutate(item_rank = min_rank(desc(item_num))) %>% 
  filter(item_rank == 1) %>% 
  knitr::kable(digits = 1)
```
```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  spread(key = order_dow, value = mean_hour) %>% 
  rename(Sunday = "0", Monday = "1", Tuesday = "2", Wednesday = "3", Thursday = "4", Friday = "5", Saturday = "6") %>% 
  knitr::kable(digit = 1)
```
### Question 2
```{r load package and data set}
library(p8105.datasets)
library(tidyverse)
library(patchwork)
data("brfss_smart2010")
```
```{r data cleaning and tidy,include=FALSE}
brfss =
  brfss_smart2010 %>%
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Poor", "Fair", "Good", "Very good", "Excellent")) %>% 
  arrange(response)
```
Answers to question 2 

1. `r names(which(brfss %>% filter(year == 2002) %>% distinct(locationabbr, locationdesc) %>% select(locationabbr) %>% table() >= 7))` states were observed at least 7 locations in 2002.`r names(which(brfss %>% filter(year == 2010) %>% distinct(locationabbr, locationdesc) %>% select(locationabbr) %>% table() >= 7))`states were observed at least 7 locations in 2010 

2.
```{r}
brfss %>%
  filter(response=="Excellent")%>%
  group_by(year, locationabbr) %>%
  summarise(mean_value = mean(data_value)) %>%
  ggplot(aes(x = year, y = mean_value, group = locationabbr, color = locationabbr)) +
  geom_line() +
  labs(
    y = "average observatons",
    title = " average observations in each state from 2002 to 2010"
  ) 
```

3.

```{r}
brfss %>%
  filter(year %in% c(2006, 2010) & locationabbr == "NY") %>%
  group_by(year,response) %>%
  ggplot(aes(x = year, y = data_value, group = response, color = response)) +
  geom_line()
```

